Mitigating Interest Flooding DDoS Attacks in Named Data Networking

### 2012-12-04 03-interest-flooding.tex
Modifying figures in evaluation
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@854 df1a90cd-247b-4364-bdaf-287a704eb499

The Interest flooding attack has two-fold effect on service quality in NDN network: it \textbf{creates network congestion} and \textbf{exhaust resources on routers}.

>>>>

The Interest flooding attack has two-fold effect on service quality in NDN network: it \emph{creates network congestion} and \emph{exhaust resources on routers}.
